\section{System requirements}
\subsection{Functional requirements}
\sysreq{1}{The system shall represent each IMU measurements as a structure containing $a_x$, $a_y$, $a_z$, $\omega_x$, $\omega_y$, $\omega_z$ and $T$.}
\sysreq{2}{The system shall convert an array of 16 bit with the least significant byte first to an accleration in $g$.}
\sysreq{3}{The system shall convert an array of 16 bit with the least significant byte first to an angular rate in $\circ/s$.}
\sysreq{4}{The system shall convert an array of 16 bit with the least significant byte first to an temperature in $\circ C$.}
\sysreq{5}{The IMU driver shall retrieve the current time when the first byte of a new IMU mesurement is received by the UART peripheral.}
\sysreq{6}{The IMU driver shall be executed in a thread separated from the main application thread.}
\sysreq{7}{The IMU driver shall write new IMU messages into a shared memory queue.}
\sysreq{8}{The IMU driver shall save the timestamp of every IMU message together with the message itself.}
\sysreq{9}{The IMU driver shall the start of a new data frame from the IMU.}
\subsection{Technical safety requirements}
\sysreq{TS1}{The IMU driver shall detect the start of an IMU message transmission from the IMU with an appropriate start byte.}
\sysreq{TS2}{The IMU driver shall represent the IMU driver status as a structure containing a status code.}
\sysreq{TS3}{The IMU driver status code shall be any of the following: OK, BUSY, NO\_DATA.}
\sysreq{TS4}{The IMU driver shall write an IMU driver status into a shared variable.}
\sysreq{TS5}{The data exchange with the OdometryApp shall contains a counter of the number of message droppped from the queue.}
\sysreq{TS6}{The IMU driver shall increment the counter of dropped message everytime a message is dropped.}
\sysreq{TS7}{The IMU driver shall set the driver status code to NO\_DATA when no data is received from the UART peripheral.}
\sysreq{TS8}{The IMU message queue shall have a fixed maximum size.}
\subsection{Non functional requirements}
\sysreq{NF1}{The IMU driver shall be implemented in C++ 17.}
